---
title: "Asian Art Museum - Periods"
author: "Diego Enriquez"
date: "9/7/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo=FALSE, warning=FALSE}
suppressMessages(library(data.table))
suppressMessages(library(lubridate))
suppressMessages(library(ggplot2))
suppressMessages(library(grid))

# Functions ==================================================================================================================================
source("asianart_func.R")
```


```{r echo=FALSE, warning=FALSE}
asianart_visitors <- readVisitorData()
asianart_visitors <- asianart_visitors[Date >= "2016-01-01"]
```

```{r echo=FALSE, warning=FALSE}
ga_allws_nochn_all <- readQueryExplorerData("data/ga/asian_allws_nochn_all.tsv", c("Date"))
ga_allws_nochn_os <- readQueryExplorerData("data/ga/asian_allws_nochn_os.tsv", c("Date"))
ga_allws_nochn_us <- readQueryExplorerData("data/ga/asian_allws_nochn_us.tsv", c("Date"))
ga_allws_nochn_do <- readQueryExplorerData("data/ga/asian_allws_nochn_do.tsv", c("Date"))
ga_allws_nochn_lo <- readQueryExplorerData("data/ga/asian_allws_nochn_lo.tsv", c("Date"))

ga_allws_chn_all <- readQueryExplorerData("data/ga/asian_allws_chn_all.tsv", c("Date", "Channel"))
ga_allws_chn_os <- readQueryExplorerData("data/ga/asian_allws_chn_os.tsv", c("Date", "Channel"))
ga_allws_chn_us <- readQueryExplorerData("data/ga/asian_allws_chn_us.tsv", c("Date", "Channel"))
ga_allws_chn_do <- readQueryExplorerData("data/ga/asian_allws_chn_do.tsv", c("Date", "Channel"))
ga_allws_chn_lo <- readQueryExplorerData("data/ga/asian_allws_chn_lo.tsv", c("Date", "Channel"))

ga_plan_nochn_all <- readQueryExplorerData("data/ga/asian_plan_nochn_all.tsv", c("Date"))
ga_plan_nochn_os <- readQueryExplorerData("data/ga/asian_plan_nochn_os.tsv", c("Date"))
ga_plan_nochn_us <- readQueryExplorerData("data/ga/asian_plan_nochn_us.tsv", c("Date"))
ga_plan_nochn_do <- readQueryExplorerData("data/ga/asian_plan_nochn_do.tsv", c("Date"))
ga_plan_nochn_lo <- readQueryExplorerData("data/ga/asian_plan_nochn_lo.tsv", c("Date"))

ga_plan_chn_all <- readQueryExplorerData("data/ga/asian_plan_chn_all.tsv", c("Date", "Channel"))
ga_plan_chn_os <- readQueryExplorerData("data/ga/asian_plan_chn_os.tsv", c("Date", "Channel"))
ga_plan_chn_us <- readQueryExplorerData("data/ga/asian_plan_chn_us.tsv", c("Date", "Channel"))
ga_plan_chn_do <- readQueryExplorerData("data/ga/asian_plan_chn_do.tsv", c("Date", "Channel"))
ga_plan_chn_lo <- readQueryExplorerData("data/ga/asian_plan_chn_lo.tsv", c("Date", "Channel"))

ga_tickets_nochn_all <- readQueryExplorerData("data/ga/asian_tickets_nochn_all.tsv", c("Date"))
ga_tickets_nochn_os <- readQueryExplorerData("data/ga/asian_tickets_nochn_os.tsv", c("Date"))
ga_tickets_nochn_us <- readQueryExplorerData("data/ga/asian_tickets_nochn_us.tsv", c("Date"))
ga_tickets_nochn_do <- readQueryExplorerData("data/ga/asian_tickets_nochn_do.tsv", c("Date"))
ga_tickets_nochn_lo <- readQueryExplorerData("data/ga/asian_tickets_nochn_lo.tsv", c("Date"))

ga_tickets_chn_all <- readQueryExplorerData("data/ga/asian_tickets_chn_all.tsv", c("Date", "Channel"))
ga_tickets_chn_os <- readQueryExplorerData("data/ga/asian_tickets_chn_os.tsv", c("Date", "Channel"))
ga_tickets_chn_us <- readQueryExplorerData("data/ga/asian_tickets_chn_us.tsv", c("Date", "Channel"))
ga_tickets_chn_do <- readQueryExplorerData("data/ga/asian_tickets_chn_do.tsv", c("Date", "Channel"))
ga_tickets_chn_lo <- readQueryExplorerData("data/ga/asian_tickets_chn_lo.tsv", c("Date", "Channel"))

ga_visit_nochn_all <- readQueryExplorerData("data/ga/asian_visit_nochn_all.tsv", c("Date"))
ga_visit_nochn_os <- readQueryExplorerData("data/ga/asian_visit_nochn_os.tsv", c("Date"))
ga_visit_nochn_us <- readQueryExplorerData("data/ga/asian_visit_nochn_us.tsv", c("Date"))
ga_visit_nochn_do <- readQueryExplorerData("data/ga/asian_visit_nochn_do.tsv", c("Date"))
ga_visit_nochn_lo <- readQueryExplorerData("data/ga/asian_visit_nochn_lo.tsv", c("Date"))

ga_visit_chn_all <- readQueryExplorerData("data/ga/asian_visit_chn_all.tsv", c("Date", "Channel"))
ga_visit_chn_os <- readQueryExplorerData("data/ga/asian_visit_chn_os.tsv", c("Date", "Channel"))
ga_visit_chn_us <- readQueryExplorerData("data/ga/asian_visit_chn_us.tsv", c("Date", "Channel"))
ga_visit_chn_do <- readQueryExplorerData("data/ga/asian_visit_chn_do.tsv", c("Date", "Channel"))
ga_visit_chn_lo <- readQueryExplorerData("data/ga/asian_visit_chn_lo.tsv", c("Date", "Channel"))

daysinfo <- data.table(Date = seq(as.Date("2016-01-01"), as.Date("2018-06-30"), by = "day"))
daysinfo$weekNum <- wday(daysinfo$Date, week_start = 1)
daysinfo$isFirstSunday <- wday(daysinfo$Date, week_start = 1) == 7 & day(daysinfo$Date) <= 7

teststart <- "2016-07-06"  # Values for Full Data
testend <- "2018-05-30"  # 31 days smaller than limit 2018-06-30
maxlag <- 31
visitordata <- asianart_visitors[Date >= teststart & Date <= as.Date(testend) + maxlag]

# Common variables
maxlag <- 15
metric <- "UniquePageviews"
```

## By Year

### 2016

```{r echo=FALSE, fig.width=10}
# teststart <- "2016-07-21"
# testend <- "2016-12-31"
# 
# visitordata <- asianart_visitors[Date >= teststart & Date <= testend]
# gamericdata <- ga_allws_chn_us[Channel == "Organic Search" & Date >= as.Date(teststart) - maxlag & Date <= as.Date(testend)]
# getMaxCorrelations(getCorrelationMatrixv2(movingAverage(gamericdata), movingAverage(visitordata), maxlag = maxlag))[11,]  # 11 UniquePageviews
# 
# plotLagComparisonv2(movingAverage(gamericdata),
#                     movingAverage(visitordata),
#                     plotstart = "2016-07-06",
#                     plotend = "2016-12-31",
#                     metric = metric,
#                     dlag = 1)
```

```{r echo=FALSE, fig.width=10}
teststart <- "2016-07-06"
testend <- "2016-12-31"

visitordata <- asianart_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_allws_chn_us[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
getMaxCorrelations(getCorrelationMatrixv2(movingAverage(gamericdata), movingAverage(visitordata), maxlag = maxlag))[11,]  # 11 UniquePageviews

plotLagComparisonv2(movingAverage(gamericdata),
                    movingAverage(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 1)
```

### 2017

```{r echo=FALSE, fig.width=10}
teststart <- "2016-12-11"
testend <- "2017-12-31"

visitordata <- asianart_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_allws_chn_us[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
getMaxCorrelations(getCorrelationMatrixv2(movingAverage(gamericdata), movingAverage(visitordata), maxlag = maxlag))[11,]  # 11 UniquePageviews

plotLagComparisonv2(movingAverage(gamericdata),
                    movingAverage(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 1)
```

### 2018

```{r echo=FALSE, fig.width=10}
teststart <- "2017-12-11"
testend <- "2018-06-30"

visitordata <- asianart_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_allws_chn_us[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
getMaxCorrelations(getCorrelationMatrixv2(movingAverage(gamericdata), movingAverage(visitordata), maxlag = maxlag))[11,]  # 11 UniquePageviews

plotLagComparisonv2(movingAverage(gamericdata),
                    movingAverage(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 1)
```

## By Season

### Summer 2016

```{r echo=FALSE, fig.width=10}
teststart <- "2016-07-06"
testend <- "2016-08-31"

visitordata <- asianart_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_allws_chn_us[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
getMaxCorrelations(getCorrelationMatrixv2(movingAverage(gamericdata), movingAverage(visitordata), maxlag = maxlag))[11,]  # 11 UniquePageviews

plotLagComparisonv2(movingAverage(gamericdata),
                    movingAverage(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 2)
```

### Summer 2017

```{r echo=FALSE, fig.width=10}
teststart <- "2017-05-11"
testend <- "2017-08-31"

visitordata <- asianart_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_allws_chn_us[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
getMaxCorrelations(getCorrelationMatrixv2(movingAverage(gamericdata), movingAverage(visitordata), maxlag = maxlag))[11,]  # 11 UniquePageviews

plotLagComparisonv2(movingAverage(gamericdata),
                    movingAverage(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 1)
```

### Summer 2018

```{r echo=FALSE, fig.width=10}
teststart <- "2018-05-11"
testend <- "2018-06-30"

visitordata <- asianart_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_allws_chn_us[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
getMaxCorrelations(getCorrelationMatrixv2(movingAverage(gamericdata), movingAverage(visitordata), maxlag = maxlag))[11,]  # 11 UniquePageviews

plotLagComparisonv2(movingAverage(gamericdata),
                    movingAverage(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 1)
```

### Autumn 2016

```{r echo=FALSE, fig.width=10}
teststart <- "2016-08-11"
testend <- "2016-11-30"

visitordata <- asianart_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_allws_chn_us[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
getMaxCorrelations(getCorrelationMatrixv2(movingAverage(gamericdata), movingAverage(visitordata), maxlag = maxlag))[11,]  # 11 UniquePageviews

plotLagComparisonv2(movingAverage(gamericdata),
                    movingAverage(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 1)
```

### Autumn 2017

```{r echo=FALSE, fig.width=10}
teststart <- "2017-08-11"
testend <- "2017-11-30"

visitordata <- asianart_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_allws_chn_us[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
getMaxCorrelations(getCorrelationMatrixv2(movingAverage(gamericdata), movingAverage(visitordata), maxlag = maxlag))[11,]  # 11 UniquePageviews

plotLagComparisonv2(movingAverage(gamericdata),
                    movingAverage(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 1)
```

### Winter 2016

```{r echo=FALSE, fig.width=10}
teststart <- "2016-11-10"
testend <- "2017-02-28"

visitordata <- asianart_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_allws_chn_us[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
getMaxCorrelations(getCorrelationMatrixv2(movingAverage(gamericdata), movingAverage(visitordata), maxlag = maxlag))[11,]  # 11 UniquePageviews

plotLagComparisonv2(movingAverage(gamericdata),
                    movingAverage(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 1)
```

### Winter 2017

```{r echo=FALSE, fig.width=10}
teststart <- "2017-11-10"
testend <- "2018-02-28"

visitordata <- asianart_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_allws_chn_us[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
getMaxCorrelations(getCorrelationMatrixv2(movingAverage(gamericdata), movingAverage(visitordata), maxlag = maxlag))[11,]  # 11 UniquePageviews

plotLagComparisonv2(movingAverage(gamericdata),
                    movingAverage(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 1)
```

### Spring 2017

```{r echo=FALSE, fig.width=10}
teststart <- "2017-02-09"
testend <- "2017-05-31"

visitordata <- asianart_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_allws_chn_us[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
getMaxCorrelations(getCorrelationMatrixv2(movingAverage(gamericdata), movingAverage(visitordata), maxlag = maxlag))[11,]  # 11 UniquePageviews

plotLagComparisonv2(movingAverage(gamericdata),
                    movingAverage(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 1)
```

### Spring 2018

```{r echo=FALSE, fig.width=10}
teststart <- "2017-02-09"
testend <- "2018-05-31"

visitordata <- asianart_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_allws_chn_us[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
getMaxCorrelations(getCorrelationMatrixv2(movingAverage(gamericdata), movingAverage(visitordata), maxlag = maxlag))[11,]  # 11 UniquePageviews

plotLagComparisonv2(movingAverage(gamericdata),
                    movingAverage(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 1)
```


## By Holidays

Source: http://www.sfusd.edu/en/news/calendars/academic-calendar.html

### Summer break 2016

```{r echo=FALSE, fig.width=10}
#teststart <- "2016-07-06"
teststart <- "2016-07-06"
testend <- "2016-08-14"

visitordata <- asianart_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_allws_chn_us[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
getMaxCorrelations(getCorrelationMatrixv2(movingAverage(gamericdata), movingAverage(visitordata), maxlag = maxlag))[11,]  # 11 UniquePageviews

plotLagComparisonv2(movingAverage(gamericdata),
                    movingAverage(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 2)
```

### Thanksgiving recess 2016

```{r echo=FALSE, fig.width=10}
#teststart <- "2016-11-23" 
teststart <- "2016-11-02" 
testend <- "2016-11-27"

visitordata <- asianart_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_allws_chn_us[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
getMaxCorrelations(getCorrelationMatrixv2(movingAverage(gamericdata), movingAverage(visitordata), maxlag = maxlag))[11,]  # 11 UniquePageviews

plotLagComparisonv2(movingAverage(gamericdata),
                    movingAverage(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 10)
```

### Winter break 2016

```{r echo=FALSE, fig.width=10}
#teststart <- "2016-12-17" 
teststart <- "2016-11-26" 
testend <- "2017-01-02"

visitordata <- asianart_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_allws_chn_us[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
getMaxCorrelations(getCorrelationMatrixv2(movingAverage(gamericdata), movingAverage(visitordata), maxlag = maxlag))[11,]  # 11 UniquePageviews

plotLagComparisonv2(movingAverage(gamericdata),
                    movingAverage(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 0)
```

### Spring break 2017

```{r echo=FALSE, fig.width=10}
#teststart <- "2017-03-25" 
teststart <- "2017-03-04" 
testend <- "2017-04-02"

visitordata <- asianart_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_allws_chn_us[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
getMaxCorrelations(getCorrelationMatrixv2(movingAverage(gamericdata), movingAverage(visitordata), maxlag = maxlag))[11,]  # 11 UniquePageviews

plotLagComparisonv2(movingAverage(gamericdata),
                    movingAverage(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 1)
```

### Summer break 2017

```{r echo=FALSE, fig.width=10}
#teststart <- "2017-05-27" 
teststart <- "2017-05-06" 
testend <- "2017-08-20"

visitordata <- asianart_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_allws_chn_us[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
getMaxCorrelations(getCorrelationMatrixv2(movingAverage(gamericdata), movingAverage(visitordata), maxlag = maxlag))[11,]  # 11 UniquePageviews

plotLagComparisonv2(movingAverage(gamericdata),
                    movingAverage(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 1)
```

### Thanksgiving recess 2017

```{r echo=FALSE, fig.width=10}
#teststart <- "2017-11-18" 
teststart <- "2017-10-28" 
testend <- "2017-11-26"

visitordata <- asianart_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_allws_chn_us[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
getMaxCorrelations(getCorrelationMatrixv2(movingAverage(gamericdata), movingAverage(visitordata), maxlag = maxlag))[11,]  # 11 UniquePageviews

plotLagComparisonv2(movingAverage(gamericdata),
                    movingAverage(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 15)
```

### Winter break 2017

```{r echo=FALSE, fig.width=10}
#teststart <- "2017-12-22" 
teststart <- "2017-12-01" 
testend <- "2018-01-07"

visitordata <- asianart_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_allws_chn_us[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
getMaxCorrelations(getCorrelationMatrixv2(movingAverage(gamericdata), movingAverage(visitordata), maxlag = maxlag))[11,]  # 11 UniquePageviews

plotLagComparisonv2(movingAverage(gamericdata),
                    movingAverage(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 0)
```

### Spring break 2018

```{r echo=FALSE, fig.width=10}
#teststart <- "2018-03-24" 
teststart <- "2018-03-03" 
testend <- "2018-04-01"

visitordata <- asianart_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_allws_chn_us[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
getMaxCorrelations(getCorrelationMatrixv2(movingAverage(gamericdata), movingAverage(visitordata), maxlag = maxlag))[11,]  # 11 UniquePageviews

plotLagComparisonv2(movingAverage(gamericdata),
                    movingAverage(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 11)
```

### Summer break 2018

```{r echo=FALSE, fig.width=10}
#eststart <- "2018-06-06" 
teststart <- "2018-05-16" 
testend <- "2018-06-30"

visitordata <- asianart_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_allws_chn_us[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
getMaxCorrelations(getCorrelationMatrixv2(movingAverage(gamericdata), movingAverage(visitordata), maxlag = maxlag))[11,]  # 11 UniquePageviews

plotLagComparisonv2(movingAverage(gamericdata),
                    movingAverage(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 2)
```


## By Month

### July 2016

```{r echo=FALSE, fig.width=10}
teststart <- "2016-07-06"
testend <- "2016-07-31"

visitordata <- asianart_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_allws_chn_us[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
getMaxCorrelations(getCorrelationMatrixv2(movingAverage(gamericdata), movingAverage(visitordata), maxlag = maxlag))[11,]  # 11 UniquePageviews

plotLagComparisonv2(movingAverage(gamericdata),
                    movingAverage(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 11)
```

### August 2016

```{r echo=FALSE, fig.width=10}
teststart <- "2016-07-11"
testend <- "2016-08-31"

visitordata <- asianart_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_allws_chn_us[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
getMaxCorrelations(getCorrelationMatrixv2(movingAverage(gamericdata), movingAverage(visitordata), maxlag = maxlag))[11,]  # 11 UniquePageviews

plotLagComparisonv2(movingAverage(gamericdata),
                    movingAverage(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 2)
```

### September 2016

```{r echo=FALSE, fig.width=10}
teststart <- "2016-08-11"
testend <- "2016-09-30"

visitordata <- asianart_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_allws_chn_us[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
getMaxCorrelations(getCorrelationMatrixv2(movingAverage(gamericdata), movingAverage(visitordata), maxlag = maxlag))[11,]  # 11 UniquePageviews

plotLagComparisonv2(movingAverage(gamericdata),
                    movingAverage(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 1)
```

### October 2016

```{r echo=FALSE, fig.width=10}
teststart <- "2016-09-10"
testend <- "2016-10-31"

visitordata <- asianart_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_allws_chn_us[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
getMaxCorrelations(getCorrelationMatrixv2(movingAverage(gamericdata), movingAverage(visitordata), maxlag = maxlag))[11,]  # 11 UniquePageviews

plotLagComparisonv2(movingAverage(gamericdata),
                    movingAverage(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 1)
```

### November 2016

```{r echo=FALSE, fig.width=10}
teststart <- "2016-10-11"
testend <- "2016-11-30"

visitordata <- asianart_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_allws_chn_us[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
getMaxCorrelations(getCorrelationMatrixv2(movingAverage(gamericdata), movingAverage(visitordata), maxlag = maxlag))[11,]  # 11 UniquePageviews

plotLagComparisonv2(movingAverage(gamericdata),
                    movingAverage(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 3)
```

### December 2016

```{r echo=FALSE, fig.width=10}
teststart <- "2016-11-10"
testend <- "2016-12-31"

visitordata <- asianart_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_allws_chn_us[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
getMaxCorrelations(getCorrelationMatrixv2(movingAverage(gamericdata), movingAverage(visitordata), maxlag = maxlag))[11,]  # 11 UniquePageviews

plotLagComparisonv2(movingAverage(gamericdata),
                    movingAverage(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 0)
```

### January 2017

```{r echo=FALSE, fig.width=10}
teststart <- "2016-12-11"
testend <- "2017-01-31"

visitordata <- asianart_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_allws_chn_us[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
getMaxCorrelations(getCorrelationMatrixv2(movingAverage(gamericdata), movingAverage(visitordata), maxlag = maxlag))[11,]  # 11 UniquePageviews

plotLagComparisonv2(movingAverage(gamericdata),
                    movingAverage(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 1)
```

### February 2017

```{r echo=FALSE, fig.width=10}
teststart <- "2017-01-11"
testend <- "2017-02-28"

visitordata <- asianart_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_allws_chn_us[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
getMaxCorrelations(getCorrelationMatrixv2(movingAverage(gamericdata), movingAverage(visitordata), maxlag = maxlag))[11,]  # 11 UniquePageviews

plotLagComparisonv2(movingAverage(gamericdata),
                    movingAverage(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 2)
```

### March 2017

```{r echo=FALSE, fig.width=10}
teststart <- "2017-02-08"
testend <- "2017-03-31"

visitordata <- asianart_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_allws_chn_us[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
getMaxCorrelations(getCorrelationMatrixv2(movingAverage(gamericdata), movingAverage(visitordata), maxlag = maxlag))[11,]  # 11 UniquePageviews

plotLagComparisonv2(movingAverage(gamericdata),
                    movingAverage(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 1)
```

### April 2017

```{r echo=FALSE, fig.width=10}
teststart <- "2017-03-11"
testend <- "2017-04-30"

visitordata <- asianart_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_allws_chn_us[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
getMaxCorrelations(getCorrelationMatrixv2(movingAverage(gamericdata), movingAverage(visitordata), maxlag = maxlag))[11,]  # 11 UniquePageviews

plotLagComparisonv2(movingAverage(gamericdata),
                    movingAverage(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 0)
```

### May 2017

```{r echo=FALSE, fig.width=10}
teststart <- "2017-04-10"
testend <- "2017-05-31"

visitordata <- asianart_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_allws_chn_us[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
getMaxCorrelations(getCorrelationMatrixv2(movingAverage(gamericdata), movingAverage(visitordata), maxlag = maxlag))[11,]  # 11 UniquePageviews

plotLagComparisonv2(movingAverage(gamericdata),
                    movingAverage(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 1)
```

### June 2017

```{r echo=FALSE, fig.width=10}
teststart <- "2017-05-11"
testend <- "2017-06-30"

visitordata <- asianart_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_allws_chn_us[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
getMaxCorrelations(getCorrelationMatrixv2(movingAverage(gamericdata), movingAverage(visitordata), maxlag = maxlag))[11,]  # 11 UniquePageviews

plotLagComparisonv2(movingAverage(gamericdata),
                    movingAverage(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 2)
```

### July 2017

```{r echo=FALSE, fig.width=10}
teststart <- "2017-06-10"
testend <- "2017-07-31"

visitordata <- asianart_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_allws_chn_us[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
getMaxCorrelations(getCorrelationMatrixv2(movingAverage(gamericdata), movingAverage(visitordata), maxlag = maxlag))[11,]  # 11 UniquePageviews

plotLagComparisonv2(movingAverage(gamericdata),
                    movingAverage(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 1)
```

### August 2017

```{r echo=FALSE, fig.width=10}
teststart <- "2017-07-11"
testend <- "2017-08-31"

visitordata <- asianart_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_allws_chn_us[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
getMaxCorrelations(getCorrelationMatrixv2(movingAverage(gamericdata), movingAverage(visitordata), maxlag = maxlag))[11,]  # 11 UniquePageviews

plotLagComparisonv2(movingAverage(gamericdata),
                    movingAverage(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 1)
```

### September 2017

```{r echo=FALSE, fig.width=10}
teststart <- "2017-08-11"
testend <- "2017-09-30"

visitordata <- asianart_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_allws_chn_us[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
getMaxCorrelations(getCorrelationMatrixv2(movingAverage(gamericdata), movingAverage(visitordata), maxlag = maxlag))[11,]  # 11 UniquePageviews

plotLagComparisonv2(movingAverage(gamericdata),
                    movingAverage(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 1)
```

### October 2017

```{r echo=FALSE, fig.width=10}
teststart <- "2017-09-10"
testend <- "2017-10-31"

visitordata <- asianart_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_allws_chn_us[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
getMaxCorrelations(getCorrelationMatrixv2(movingAverage(gamericdata), movingAverage(visitordata), maxlag = maxlag))[11,]  # 11 UniquePageviews

plotLagComparisonv2(movingAverage(gamericdata),
                    movingAverage(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 0)
```

### November 2017

```{r echo=FALSE, fig.width=10}
teststart <- "2017-10-11"
testend <- "2017-11-30"

visitordata <- asianart_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_allws_chn_us[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
getMaxCorrelations(getCorrelationMatrixv2(movingAverage(gamericdata), movingAverage(visitordata), maxlag = maxlag))[11,]  # 11 UniquePageviews

plotLagComparisonv2(movingAverage(gamericdata),
                    movingAverage(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 1)
```

### December 2017

```{r echo=FALSE, fig.width=10}
teststart <- "2017-11-10"
testend <- "2017-12-31"

visitordata <- asianart_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_allws_chn_us[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
getMaxCorrelations(getCorrelationMatrixv2(movingAverage(gamericdata), movingAverage(visitordata), maxlag = maxlag))[11,]  # 11 UniquePageviews

plotLagComparisonv2(movingAverage(gamericdata),
                    movingAverage(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 1)
```

### January 2018

```{r echo=FALSE, fig.width=10}
teststart <- "2017-12-11"
testend <- "2018-01-31"

visitordata <- asianart_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_allws_chn_us[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
getMaxCorrelations(getCorrelationMatrixv2(movingAverage(gamericdata), movingAverage(visitordata), maxlag = maxlag))[11,]  # 11 UniquePageviews

plotLagComparisonv2(movingAverage(gamericdata),
                    movingAverage(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 0)
```

### February 2018

```{r echo=FALSE, fig.width=10}
teststart <- "2018-01-11"
testend <- "2018-02-28"

visitordata <- asianart_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_allws_chn_us[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
getMaxCorrelations(getCorrelationMatrixv2(movingAverage(gamericdata), movingAverage(visitordata), maxlag = maxlag))[11,]  # 11 UniquePageviews

plotLagComparisonv2(movingAverage(gamericdata),
                    movingAverage(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 1)
```

### March 2018

```{r echo=FALSE, fig.width=10}
teststart <- "2018-02-08"
testend <- "2018-03-31"

visitordata <- asianart_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_allws_chn_us[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
getMaxCorrelations(getCorrelationMatrixv2(movingAverage(gamericdata), movingAverage(visitordata), maxlag = maxlag))[11,]  # 11 UniquePageviews

plotLagComparisonv2(movingAverage(gamericdata),
                    movingAverage(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 3)
```

### April 2018

```{r echo=FALSE, fig.width=10}
teststart <- "2018-03-11"
testend <- "2018-04-30"

visitordata <- asianart_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_allws_chn_us[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
getMaxCorrelations(getCorrelationMatrixv2(movingAverage(gamericdata), movingAverage(visitordata), maxlag = maxlag))[11,]  # 11 UniquePageviews

plotLagComparisonv2(movingAverage(gamericdata),
                    movingAverage(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 0)
```

### May 2018

```{r echo=FALSE, fig.width=10}
teststart <- "2018-04-10"
testend <- "2018-05-31"

visitordata <- asianart_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_allws_chn_us[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
getMaxCorrelations(getCorrelationMatrixv2(movingAverage(gamericdata), movingAverage(visitordata), maxlag = maxlag))[11,]  # 11 UniquePageviews

plotLagComparisonv2(movingAverage(gamericdata),
                    movingAverage(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 3)
```

### June 2018

```{r echo=FALSE, fig.width=10}
teststart <- "2018-05-11"
testend <- "2018-06-30"

visitordata <- asianart_visitors[Date >= as.Date(teststart) + maxlag & Date <= testend]
gamericdata <- ga_allws_chn_us[Channel == "Organic Search" & Date >= teststart & Date <= as.Date(testend)]
getMaxCorrelations(getCorrelationMatrixv2(movingAverage(gamericdata), movingAverage(visitordata), maxlag = maxlag))[11,]  # 11 UniquePageviews

plotLagComparisonv2(movingAverage(gamericdata),
                    movingAverage(visitordata),
                    plotstart = teststart,
                    plotend = testend,
                    metric = metric,
                    dlag = 1)
```

