---
title: "Asian Art Museum - Best Correlations"
author: "Diego Enriquez"
date: "9/7/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo=FALSE, warning=FALSE}
suppressMessages(library(data.table))
suppressMessages(library(lubridate))
suppressMessages(library(ggplot2))
suppressMessages(library(grid))

# Functions ==================================================================================================================================
source("asianart_func.R")
```


```{r echo=FALSE, warning=FALSE}
asianart_visitors <- readVisitorData()
asianart_visitors <- asianart_visitors[Date >= "2016-01-01"]
```

```{r echo=FALSE, warning=FALSE}
ga_allws_nochn_all <- readQueryExplorerData("data/ga/asian_allws_nochn_all.tsv", c("Date"))
ga_allws_nochn_os <- readQueryExplorerData("data/ga/asian_allws_nochn_os.tsv", c("Date"))
ga_allws_nochn_us <- readQueryExplorerData("data/ga/asian_allws_nochn_us.tsv", c("Date"))
ga_allws_nochn_do <- readQueryExplorerData("data/ga/asian_allws_nochn_do.tsv", c("Date"))
ga_allws_nochn_lo <- readQueryExplorerData("data/ga/asian_allws_nochn_lo.tsv", c("Date"))

ga_allws_chn_all <- readQueryExplorerData("data/ga/asian_allws_chn_all.tsv", c("Date", "Channel"))
ga_allws_chn_os <- readQueryExplorerData("data/ga/asian_allws_chn_os.tsv", c("Date", "Channel"))
ga_allws_chn_us <- readQueryExplorerData("data/ga/asian_allws_chn_us.tsv", c("Date", "Channel"))
ga_allws_chn_do <- readQueryExplorerData("data/ga/asian_allws_chn_do.tsv", c("Date", "Channel"))
ga_allws_chn_lo <- readQueryExplorerData("data/ga/asian_allws_chn_lo.tsv", c("Date", "Channel"))

ga_plan_nochn_all <- readQueryExplorerData("data/ga/asian_plan_nochn_all.tsv", c("Date"))
ga_plan_nochn_os <- readQueryExplorerData("data/ga/asian_plan_nochn_os.tsv", c("Date"))
ga_plan_nochn_us <- readQueryExplorerData("data/ga/asian_plan_nochn_us.tsv", c("Date"))
ga_plan_nochn_do <- readQueryExplorerData("data/ga/asian_plan_nochn_do.tsv", c("Date"))
ga_plan_nochn_lo <- readQueryExplorerData("data/ga/asian_plan_nochn_lo.tsv", c("Date"))

ga_plan_chn_all <- readQueryExplorerData("data/ga/asian_plan_chn_all.tsv", c("Date", "Channel"))
ga_plan_chn_os <- readQueryExplorerData("data/ga/asian_plan_chn_os.tsv", c("Date", "Channel"))
ga_plan_chn_us <- readQueryExplorerData("data/ga/asian_plan_chn_us.tsv", c("Date", "Channel"))
ga_plan_chn_do <- readQueryExplorerData("data/ga/asian_plan_chn_do.tsv", c("Date", "Channel"))
ga_plan_chn_lo <- readQueryExplorerData("data/ga/asian_plan_chn_lo.tsv", c("Date", "Channel"))

ga_tickets_nochn_all <- readQueryExplorerData("data/ga/asian_tickets_nochn_all.tsv", c("Date"))
ga_tickets_nochn_os <- readQueryExplorerData("data/ga/asian_tickets_nochn_os.tsv", c("Date"))
ga_tickets_nochn_us <- readQueryExplorerData("data/ga/asian_tickets_nochn_us.tsv", c("Date"))
ga_tickets_nochn_do <- readQueryExplorerData("data/ga/asian_tickets_nochn_do.tsv", c("Date"))
ga_tickets_nochn_lo <- readQueryExplorerData("data/ga/asian_tickets_nochn_lo.tsv", c("Date"))

ga_tickets_chn_all <- readQueryExplorerData("data/ga/asian_tickets_chn_all.tsv", c("Date", "Channel"))
ga_tickets_chn_os <- readQueryExplorerData("data/ga/asian_tickets_chn_os.tsv", c("Date", "Channel"))
ga_tickets_chn_us <- readQueryExplorerData("data/ga/asian_tickets_chn_us.tsv", c("Date", "Channel"))
ga_tickets_chn_do <- readQueryExplorerData("data/ga/asian_tickets_chn_do.tsv", c("Date", "Channel"))
ga_tickets_chn_lo <- readQueryExplorerData("data/ga/asian_tickets_chn_lo.tsv", c("Date", "Channel"))

ga_visit_nochn_all <- readQueryExplorerData("data/ga/asian_visit_nochn_all.tsv", c("Date"))
ga_visit_nochn_os <- readQueryExplorerData("data/ga/asian_visit_nochn_os.tsv", c("Date"))
ga_visit_nochn_us <- readQueryExplorerData("data/ga/asian_visit_nochn_us.tsv", c("Date"))
ga_visit_nochn_do <- readQueryExplorerData("data/ga/asian_visit_nochn_do.tsv", c("Date"))
ga_visit_nochn_lo <- readQueryExplorerData("data/ga/asian_visit_nochn_lo.tsv", c("Date"))

ga_visit_chn_all <- readQueryExplorerData("data/ga/asian_visit_chn_all.tsv", c("Date", "Channel"))
ga_visit_chn_os <- readQueryExplorerData("data/ga/asian_visit_chn_os.tsv", c("Date", "Channel"))
ga_visit_chn_us <- readQueryExplorerData("data/ga/asian_visit_chn_us.tsv", c("Date", "Channel"))
ga_visit_chn_do <- readQueryExplorerData("data/ga/asian_visit_chn_do.tsv", c("Date", "Channel"))
ga_visit_chn_lo <- readQueryExplorerData("data/ga/asian_visit_chn_lo.tsv", c("Date", "Channel"))

daysinfo <- data.table(Date = seq(as.Date("2016-01-01"), as.Date("2018-06-30"), by = "day"))
daysinfo$weekNum <- wday(daysinfo$Date, week_start = 1)
daysinfo$isFirstSunday <- wday(daysinfo$Date, week_start = 1) == 7 & day(daysinfo$Date) <= 7

teststart <- "2016-07-06"  # Values for Full Data
testend <- "2018-05-30"  # 31 days smaller than limit 2018-06-30
maxlag <- 31
visitordata <- asianart_visitors[Date >= teststart & Date <= as.Date(testend) + maxlag]
```

```{r echo=FALSE, fig.width=10}
# plotCorrelations(getCorrelationMatrix(gametrics = ga_allws_chn_all[Channel == "Organic Search" & Date >= teststart & Date <= testend],
#                                       visitors = visitordata),
#                  select = "UniquePageviews",
#                  plottitle = "")
# 
# plotCorrelations(getCorrelationMatrix(gametrics = movingAverage(ga_allws_chn_all[Channel == "Organic Search" & Date >= teststart & Date <= testend]),
#                                       visitors = movingAverage(visitordata)),
#                  select = "UniquePageviews",
#                  plottitle = "")

# plotCorrelations(getCorrelationMatrix(gametrics = movingAverage(GA_tk_us[Date >= teststart & Date <= testend]),
#                                       visitors = movingAverage(visitordata)),
#                  select = "Pageviews",
#                  plottitle = "")
```

```{r echo=FALSE, fig.width=10}
# plotLagComparison(movingAverage(ga_allws_chn_all[Channel == "Organic Search" & Date >= teststart & Date <= testend]),
#                     movingAverage(visitordata),
#                     metric = "UniquePageviews",
#                     dlag = 1)
# 
# plotLagComparisonSameSacle(movingAverage(ga_allws_chn_all[Channel == "Organic Search" & Date >= teststart & Date <= testend]),
#                     movingAverage(visitordata),
#                     metric = "UniquePageviews",
#                     dlag = 1)
```

## All Web Site

#### United States, Organic Search, UniquePageviews, corr: 0.837

```{r echo=FALSE, fig.width=10, warning=FALSE}
plotLagComparison(movingAverage(ga_allws_chn_us[Channel == "Organic Search" & Date >= teststart & Date <= testend]),
                    movingAverage(visitordata),
                    metric = "UniquePageviews",
                    dlag = 1)
```

```{r echo=FALSE, fig.width=10, fig.height=2.5, warning=FALSE}
plotLagComparisonSameSacle(movingAverage(ga_allws_chn_us[Channel == "Organic Search" & Date >= teststart & Date <= testend]),
                    movingAverage(visitordata),
                    metric = "UniquePageviews",
                    dlag = 1)
```

```{r echo=FALSE, fig.width=10, fig.height=2.5, warning=FALSE}
plotCorrelations(getCorrelationMatrix(gametrics = movingAverage(ga_allws_chn_us[Channel == "Organic Search" & Date >= teststart & Date <= testend]),
                                      visitors = movingAverage(visitordata)),
                 select = "UniquePageviews",
                 plottitle = "")
```

#### Without moving average

```{r echo=FALSE, fig.width=10, warning=FALSE}
plotLagComparison(ga_allws_chn_us[Channel == "Organic Search" & Date >= teststart & Date <= testend],
                    visitordata,
                    metric = "UniquePageviews",
                    dlag = 1)
```

#### Without moving average, zoom 

Lightblue lines show Sundays, Red lines show first Sundays each month.

#### Zoom Jul 2016 - Dec 2016, lag 0

```{r echo=FALSE, fig.width=10, fig.height=2.5, warning=FALSE}
ggplot(asianart_visitors, aes(Date, visitors)) +
  geom_line(size = 0.5, col = "grey40") +
  #geom_line(data = movingAverage(asianart_visitors), aes(Date, visitors), size = 0.5, col = "blue") +
  geom_vline(xintercept = daysinfo[weekNum == 7, Date], col = "lightblue", lty = 2) +
  geom_vline(xintercept = daysinfo[isFirstSunday == TRUE, Date], col = "red", lty = 2) +
  theme_bw() +
  labs(title = "Asian Art Museum visits") +
  coord_cartesian(xlim = as.Date(c("2016-07-06", "2017-01-10")))
```

```{r echo=FALSE, fig.width=10, fig.height=2.5, warning=FALSE}
ggplot(ga_allws_chn_us[Channel == "Organic Search"], aes(Date, UniquePageviews)) +
  geom_line(size = 0.5, col = "grey40") +
  #geom_line(data = movingAverage(asianart_visitors), aes(Date, visitors), size = 0.5, col = "blue") +
  geom_vline(xintercept = daysinfo[weekNum == 7, Date], col = "lightblue", lty = 2) +
  geom_vline(xintercept = daysinfo[isFirstSunday == TRUE, Date], col = "red", lty = 2) +
  theme_bw() +
  labs(title = "Asian Art Museum GA metric") +
  coord_cartesian(xlim = as.Date(c("2016-07-06", "2017-01-10")))
```

#### Zoom Jan 2017 - Jun 2017, lag 0

```{r echo=FALSE, fig.width=10, fig.height=2.5, warning=FALSE}
ggplot(asianart_visitors, aes(Date, visitors)) +
  geom_line(size = 0.5, col = "grey40") +
  #geom_line(data = movingAverage(asianart_visitors), aes(Date, visitors), size = 0.5, col = "blue") +
  geom_vline(xintercept = daysinfo[weekNum == 7, Date], col = "lightblue", lty = 2) +
  geom_vline(xintercept = daysinfo[isFirstSunday == TRUE, Date], col = "red", lty = 2) +
  theme_bw() +
  labs(title = "Asian Art Museum visits") +
  coord_cartesian(xlim = as.Date(c("2017-01-01", "2017-07-15")))
```

```{r echo=FALSE, fig.width=10, fig.height=2.5, warning=FALSE}
ggplot(ga_allws_chn_us[Channel == "Organic Search"], aes(Date, UniquePageviews)) +
  geom_line(size = 0.5, col = "grey40") +
  #geom_line(data = movingAverage(asianart_visitors), aes(Date, visitors), size = 0.5, col = "blue") +
  geom_vline(xintercept = daysinfo[weekNum == 7, Date], col = "lightblue", lty = 2) +
  geom_vline(xintercept = daysinfo[isFirstSunday == TRUE, Date], col = "red", lty = 2) +
  theme_bw() +
  labs(title = "Asian Art Museum GA metric") +
  coord_cartesian(xlim = as.Date(c("2017-01-01", "2017-07-15")))
```

#### Zoom Jun 2017 - Dec 2017, lag 0

```{r echo=FALSE, fig.width=10, fig.height=2.5, warning=FALSE}
ggplot(asianart_visitors, aes(Date, visitors)) +
  geom_line(size = 0.5, col = "grey40") +
  #geom_line(data = movingAverage(asianart_visitors), aes(Date, visitors), size = 0.5, col = "blue") +
  geom_vline(xintercept = daysinfo[weekNum == 7, Date], col = "lightblue", lty = 2) +
  geom_vline(xintercept = daysinfo[isFirstSunday == TRUE, Date], col = "red", lty = 2) +
  theme_bw() +
  labs(title = "Asian Art Museum visits") +
  coord_cartesian(xlim = as.Date(c("2017-07-01", "2018-01-10")))
```

```{r echo=FALSE, fig.width=10, fig.height=2.5, warning=FALSE}
ggplot(ga_allws_chn_us[Channel == "Organic Search"], aes(Date, UniquePageviews)) +
  geom_line(size = 0.5, col = "grey40") +
  #geom_line(data = movingAverage(asianart_visitors), aes(Date, visitors), size = 0.5, col = "blue") +
  geom_vline(xintercept = daysinfo[weekNum == 7, Date], col = "lightblue", lty = 2) +
  geom_vline(xintercept = daysinfo[isFirstSunday == TRUE, Date], col = "red", lty = 2) +
  theme_bw() +
  labs(title = "Asian Art Museum GA metric") +
  coord_cartesian(xlim = as.Date(c("2017-07-01", "2018-01-10")))
```

#### Zoom Jan 2018 - Jun 2018, lag 0

```{r echo=FALSE, fig.width=10, fig.height=2.5, warning=FALSE}
ggplot(asianart_visitors, aes(Date, visitors)) +
  geom_line(size = 0.5, col = "grey40") +
  #geom_line(data = movingAverage(asianart_visitors), aes(Date, visitors), size = 0.5, col = "blue") +
  geom_vline(xintercept = daysinfo[weekNum == 7, Date], col = "lightblue", lty = 2) +
  geom_vline(xintercept = daysinfo[isFirstSunday == TRUE, Date], col = "red", lty = 2) +
  theme_bw() +
  labs(title = "Asian Art Museum visits") +
  coord_cartesian(xlim = as.Date(c("2018-01-01", "2018-06-30")))
```

```{r echo=FALSE, fig.width=10, fig.height=2.5, warning=FALSE}
ggplot(ga_allws_chn_us[Channel == "Organic Search"], aes(Date, UniquePageviews)) +
  geom_line(size = 0.5, col = "grey40") +
  #geom_line(data = movingAverage(asianart_visitors), aes(Date, visitors), size = 0.5, col = "blue") +
  geom_vline(xintercept = daysinfo[weekNum == 7, Date], col = "lightblue", lty = 2) +
  geom_vline(xintercept = daysinfo[isFirstSunday == TRUE, Date], col = "red", lty = 2) +
  theme_bw() +
  labs(title = "Asian Art Museum GA metric") +
  coord_cartesian(xlim = as.Date(c("2018-01-01", "2018-06-30")))
```


#### All locations, Organic Search, UniquePageviews, corr: 0.830

```{r echo=FALSE, fig.width=10, warning=FALSE}
plotLagComparison(movingAverage(ga_allws_chn_all[Channel == "Organic Search" & Date >= teststart & Date <= testend]),
                    movingAverage(visitordata),
                    metric = "UniquePageviews",
                    dlag = 1)
```

```{r echo=FALSE, fig.width=10, fig.height=2.5, warning=FALSE}
plotLagComparisonSameSacle(movingAverage(ga_allws_chn_all[Channel == "Organic Search" & Date >= teststart & Date <= testend]),
                    movingAverage(visitordata),
                    metric = "UniquePageviews",
                    dlag = 1)
```

```{r echo=FALSE, fig.width=10, fig.height=2.5, warning=FALSE}
plotCorrelations(getCorrelationMatrix(gametrics = movingAverage(ga_allws_chn_all[Channel == "Organic Search" & Date >= teststart & Date <= testend]),
                                      visitors = movingAverage(visitordata)),
                 select = "UniquePageviews",
                 plottitle = "")
```

#### Domestics, Organic Search, UniquePageviews, corr: 0.819

```{r echo=FALSE, fig.width=10, warning=FALSE}
plotLagComparison(movingAverage(ga_allws_chn_do[Channel == "Organic Search" & Date >= teststart & Date <= testend]),
                    movingAverage(visitordata),
                    metric = "UniquePageviews",
                    dlag = 1)
```

```{r echo=FALSE, fig.width=10, fig.height=2.5, warning=FALSE}
plotLagComparisonSameSacle(movingAverage(ga_allws_chn_do[Channel == "Organic Search" & Date >= teststart & Date <= testend]),
                    movingAverage(visitordata),
                    metric = "UniquePageviews",
                    dlag = 1)
```

```{r echo=FALSE, fig.width=10, fig.height=2.5, warning=FALSE}
plotCorrelations(getCorrelationMatrix(gametrics = movingAverage(ga_allws_chn_do[Channel == "Organic Search" & Date >= teststart & Date <= testend]),
                                      visitors = movingAverage(visitordata)),
                 select = "UniquePageviews",
                 plottitle = "")
```


## Plan your visit

#### All locations, Organic Search, Users, corr: 0.792

```{r echo=FALSE, fig.width=10, warning=FALSE}
plotLagComparison(movingAverage(ga_plan_chn_all[Channel == "Organic Search" & Date >= teststart & Date <= testend]),
                    movingAverage(visitordata),
                    metric = "Users",
                    dlag = 1)
```

```{r echo=FALSE, fig.width=10, fig.height=2.5, warning=FALSE}
plotLagComparisonSameSacle(movingAverage(ga_plan_chn_all[Channel == "Organic Search" & Date >= teststart & Date <= testend]),
                    movingAverage(visitordata),
                    metric = "Users",
                    dlag = 1)
```

```{r echo=FALSE, fig.width=10, fig.height=2.5, warning=FALSE}
plotCorrelations(getCorrelationMatrix(gametrics = movingAverage(ga_plan_chn_all[Channel == "Organic Search" & Date >= teststart & Date <= testend]),
                                      visitors = movingAverage(visitordata)),
                 select = "Users",
                 plottitle = "")
```

#### United States, Organic Search, UniquePageviews, corr: 0.792

```{r echo=FALSE, fig.width=10, warning=FALSE}
plotLagComparison(movingAverage(ga_plan_chn_us[Channel == "Organic Search" & Date >= teststart & Date <= testend]),
                    movingAverage(visitordata),
                    metric = "UniquePageviews",
                    dlag = 1)
```

```{r echo=FALSE, fig.width=10, fig.height=2.5, warning=FALSE}
plotLagComparisonSameSacle(movingAverage(ga_plan_chn_us[Channel == "Organic Search" & Date >= teststart & Date <= testend]),
                    movingAverage(visitordata),
                    metric = "UniquePageviews",
                    dlag = 1)
```

```{r echo=FALSE, fig.width=10, fig.height=2.5, warning=FALSE}
plotCorrelations(getCorrelationMatrix(gametrics = movingAverage(ga_plan_chn_us[Channel == "Organic Search" & Date >= teststart & Date <= testend]),
                                      visitors = movingAverage(visitordata)),
                 select = "UniquePageviews",
                 plottitle = "")
```

#### Domestics, Organic Search, Users, corr: 0.779

```{r echo=FALSE, fig.width=10, warning=FALSE}
plotLagComparison(movingAverage(ga_plan_chn_do[Channel == "Organic Search" & Date >= teststart & Date <= testend]),
                    movingAverage(visitordata),
                    metric = "Users",
                    dlag = 1)
```

```{r echo=FALSE, fig.width=10, fig.height=2.5, warning=FALSE}
plotLagComparisonSameSacle(movingAverage(ga_plan_chn_do[Channel == "Organic Search" & Date >= teststart & Date <= testend]),
                    movingAverage(visitordata),
                    metric = "Users",
                    dlag = 1)
```

```{r echo=FALSE, fig.width=10, fig.height=2.5, warning=FALSE}
plotCorrelations(getCorrelationMatrix(gametrics = movingAverage(ga_plan_chn_do[Channel == "Organic Search" & Date >= teststart & Date <= testend]),
                                      visitors = movingAverage(visitordata)),
                 select = "Users",
                 plottitle = "")
```


## Tickets

#### United States, Organic Search, Users, corr: 0.822

```{r echo=FALSE, fig.width=10, warning=FALSE}
plotLagComparison(movingAverage(ga_tickets_chn_us[Channel == "Organic Search" & Date >= teststart & Date <= testend]),
                    movingAverage(visitordata),
                    metric = "Users",
                    dlag = 1)
```

```{r echo=FALSE, fig.width=10, fig.height=2.5, warning=FALSE}
plotLagComparisonSameSacle(movingAverage(ga_tickets_chn_us[Channel == "Organic Search" & Date >= teststart & Date <= testend]),
                    movingAverage(visitordata),
                    metric = "Users",
                    dlag = 1)
```

```{r echo=FALSE, fig.width=10, fig.height=2.5, warning=FALSE}
plotCorrelations(getCorrelationMatrix(gametrics = movingAverage(ga_tickets_chn_us[Channel == "Organic Search" & Date >= teststart & Date <= testend]),
                                      visitors = movingAverage(visitordata)),
                 select = "Users",
                 plottitle = "")
```

#### United States, All channels, UsersOld, corr: 0.819

```{r echo=FALSE, fig.width=10, warning=FALSE}
plotLagComparison(movingAverage(ga_tickets_nochn_us[Date >= teststart & Date <= testend]),
                    movingAverage(visitordata),
                    metric = "UsersOld",
                    dlag = 1)
```

```{r echo=FALSE, fig.width=10, fig.height=2.5, warning=FALSE}
plotLagComparisonSameSacle(movingAverage(ga_tickets_nochn_us[Date >= teststart & Date <= testend]),
                    movingAverage(visitordata),
                    metric = "UsersOld",
                    dlag = 1)
```

```{r echo=FALSE, fig.width=10, fig.height=2.5, warning=FALSE}
plotCorrelations(getCorrelationMatrix(gametrics = movingAverage(ga_tickets_nochn_us[Date >= teststart & Date <= testend]),
                                      visitors = movingAverage(visitordata)),
                 select = "UsersOld",
                 plottitle = "")
```

#### All locations, Organic Search, Users, corr: 0.819

```{r echo=FALSE, fig.width=10, warning=FALSE}
plotLagComparison(movingAverage(ga_tickets_chn_all[Channel == "Organic Search" & Date >= teststart & Date <= testend]),
                    movingAverage(visitordata),
                    metric = "Users",
                    dlag = 1)
```

```{r echo=FALSE, fig.width=10, fig.height=2.5, warning=FALSE}
plotLagComparisonSameSacle(movingAverage(ga_tickets_chn_all[Channel == "Organic Search" & Date >= teststart & Date <= testend]),
                    movingAverage(visitordata),
                    metric = "Users",
                    dlag = 1)
```

```{r echo=FALSE, fig.width=10, fig.height=2.5, warning=FALSE}
plotCorrelations(getCorrelationMatrix(gametrics = movingAverage(ga_tickets_chn_all[Channel == "Organic Search" & Date >= teststart & Date <= testend]),
                                      visitors = movingAverage(visitordata)),
                 select = "Users",
                 plottitle = "")
```


## Visit

#### United States, All channels, Sessions, corr: 0.789

```{r echo=FALSE, fig.width=10, warning=FALSE}
plotLagComparison(movingAverage(ga_visit_nochn_us[Date >= teststart & Date <= testend]),
                    movingAverage(visitordata),
                    metric = "Sessions",
                    dlag = 2)
```

```{r echo=FALSE, fig.width=10, fig.height=2.5, warning=FALSE}
plotLagComparisonSameSacle(movingAverage(ga_visit_nochn_us[Date >= teststart & Date <= testend]),
                    movingAverage(visitordata),
                    metric = "Sessions",
                    dlag = 2)
```

```{r echo=FALSE, fig.width=10, fig.height=2.5, warning=FALSE}
plotCorrelations(getCorrelationMatrix(gametrics = movingAverage(ga_visit_nochn_us[Date >= teststart & Date <= testend]),
                                      visitors = movingAverage(visitordata)),
                 select = "Sessions",
                 plottitle = "")
```

#### United States, Organic Search, Sessions, corr: 0.788

```{r echo=FALSE, fig.width=10, warning=FALSE}
plotLagComparison(movingAverage(ga_visit_chn_us[Channel == "Organic Search" & Date >= teststart & Date <= testend]),
                    movingAverage(visitordata),
                    metric = "Sessions",
                    dlag = 2)
```

```{r echo=FALSE, fig.width=10, fig.height=2.5, warning=FALSE}
plotLagComparisonSameSacle(movingAverage(ga_visit_chn_us[Channel == "Organic Search" & Date >= teststart & Date <= testend]),
                    movingAverage(visitordata),
                    metric = "Sessions",
                    dlag = 2)
```

```{r echo=FALSE, fig.width=10, fig.height=2.5, warning=FALSE}
plotCorrelations(getCorrelationMatrix(gametrics = movingAverage(ga_visit_chn_us[Channel == "Organic Search" & Date >= teststart & Date <= testend]),
                                      visitors = movingAverage(visitordata)),
                 select = "Sessions",
                 plottitle = "")
```

#### All locations, All channels, Sessions, corr: 0.779

```{r echo=FALSE, fig.width=10, warning=FALSE}
plotLagComparison(movingAverage(ga_visit_nochn_all[Date >= teststart & Date <= testend]),
                    movingAverage(visitordata),
                    metric = "Sessions",
                    dlag = 2)
```

```{r echo=FALSE, fig.width=10, fig.height=2.5, warning=FALSE}
plotLagComparisonSameSacle(movingAverage(ga_visit_nochn_all[Date >= teststart & Date <= testend]),
                    movingAverage(visitordata),
                    metric = "Sessions",
                    dlag = 2)
```

```{r echo=FALSE, fig.width=10, fig.height=2.5, warning=FALSE}
plotCorrelations(getCorrelationMatrix(gametrics = movingAverage(ga_visit_nochn_all[Date >= teststart & Date <= testend]),
                                      visitors = movingAverage(visitordata)),
                 select = "Sessions",
                 plottitle = "")
```